[---]  |         ^    |\     |  []
|   |  |        / \   | \    |  []
[---]  |       |---|  |  \   |  []
|      |      /    \  |   \  |  
|      [--- /       \ |    \ |  []

This is my plan on my Phaser > GraviTraxSim.html!
- i also make video's about this so uhhhh, future me i hope you can read this thingy-magingy

- everything till now works

- right bar plan {
    - icons on the right side
    - when on hover, it grows a little bit!
    - when clicked, it gets selected and stays big plus goes to the side and 5px away from the bar, ya know what i mean!
    - when another icon is clicked, the previous one goes back to normal and the new one gets selected
    - the selected icon can be clicked again but nothing wont happe of course!
    - in the future, when there are too many pieces/icons we will have arrows to go to a new thing what contains different things!
}
- survival mode {
    - you need to get the ball to the finish and building your own track by earning money, the more time the track takes and the cooler it looks the more money you will get!
    
    - in the game a start and finish are free. But everything else costs money! 
    - each piece costs its amount what shows in the bottom-right of the icon and the amount shows in the bottom-left of the icon!
    - you will have a balance and you will see it on the top-right of the screen!
    - every 10_min you have option to get a rebirth point for 10 [money]!
    - and you can withdraw upto 100 [money] at a time!
    - your rebirth points will be used for rebirthing your track and money!
    - but you can load and save your track anytime!
    - that means you can also play a survival track in creative mode, just remember, in survival you can only load a schematic!
    - a rebirth point also gives some powers, mostly income multiplyer and more availible pieces!
}
- load/save system {
    - you can load and save your track anytime!

    - in survival mode you can only load a schematic! If you log in with a account you can share your track with others and go to there's!
    - even without a account it will save 
    - with a account you can save your track very efficiently and more settings and sometimes save it to the cloud!
    - you can also make your track public so others can play it!
    - you can even share a survival track for extra impressivnes
    - also there is a like/dislike system!
    - also when you have account you have a profile picture and name!
    - you can also see other people's profile and their tracks!
    - you can also message other players!
    - you can also gift other players [money]!
    - also with likes you can unlock astethics, like a new marble color or something!
}
- chatGTS {
    - a chatbot! Btw it will be named chatGTS, because chatGraviTraxSimulator!
    - it will be able to answer questions and give tips and stuff!
    - it will also be able to edit your track, like suggest a piece or something!
    - it will also be able to give you tips on how to improve your track!
    - it can also read your track!!!
    - its locked in survival mode!
    - the most hardest thing to earn is this chatGTS at a 1000 likes, every time my game populates it will grow the price!
    - also only availible with a accou